Seminar paper on Probabilistic Near-Duplicate Detection Using Simhash

### 2019-07-09 ii/paper/paper.tex
Restructuring and fixing syntax

\begin{figure}[H]
    \includegraphics[scale=0.4]{./gfx/distribution.png}
    \centering
    \caption{Histogram of \emph{simhash} weights. A clear trend towards a Laplace-like distribution can be seen in a\).}\label{fig:weight-distribution}
\end{figure}

@@

\begin{lemma1}
If two sets $S_1, S_2$ of the same size $h$ differ in exactly 1 bit and $S_1 \prec S_2$, then $∀u : p(u, S_1) \geq p(u, S_2)$.
\end{lemma1}

@@

While using VOSH for probabilistic search a new problems become apparent that have not been addressed yet.
VOSH is not and cannot be capable of deciding, which of two siblings at each level is more optimal.
To solve this problem, the authors of~\cite{inproc:main} introduce an additional data structure $M$, which is a max-heap operating on a key-value pairs.
The key is the probability of flips in page $u$ for set $S$, while the value is the actual value $S$.
M is populated with tuples generated by the $h$ root nodes of VOSH trees.

@@

\begin{figure}[H]
    \includegraphics[scale=0.35]{./gfx/vosh-performance.png}
    \centering
    \caption{Performance results comparing random comparison search and volatility order based search.}\label{fig:vosh-performance}
\end{figure}

>>>>

\begin{figure}[H]
    \includegraphics[scale=0.4]{./gfx/distribution.png}
    \centering
    \caption{Histogram of \emph{simhash} weights. A clear trend towards a Laplace-like distribution can be seen in (a).}\label{fig:weight-distribution}
\end{figure}

@@

\begin{lemma1}
If two sets $S_1, S_2$ of the same size $h$ differ in exactly 1 bit and $S_1 \prec S_2$, then $\forall u : p(u, S_1) \geq p(u, S_2)$.
\end{lemma1}

@@

While using VOSH for probabilistic search a new problems become apparent that have not been addressed yet.
VOSH is not and cannot be capable of deciding, which of two siblings at each level is more optimal.
To solve this problem, the authors of~\cite{inproc:main} introduce an additional data structure $M$, which is a max-heap operating on a key-value pairs.

\begin{figure}[H]
    \includegraphics[scale=0.33]{./gfx/vosh-performance.png}
    \centering
    \caption{Performance results comparing random comparison search and volatility order based search.}\label{fig:vosh-performance}
\end{figure}

The key is the probability of flips in page $u$ for set $S$, while the value is the actual value $S$.
M is populated with tuples generated by the $h$ root nodes of VOSH trees.

@@

It is notable, that the random approach needs 64 flips to get a 100\% recall for all hamming distances.
This is to be expected, but still shows how inefficient such an approach would be.

Also it becomes apparent that the speedup for VOSH in comparison to a random approach gets higher, the bigger the Hamming distance $h$ gets, making it viable for larger hash sizes with proportional small Hamming distances.

\subsection{Online Mode}
